Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-09-10 pnas/Towards.tex
small update of the acknowledgment

\section*{Acknowledgment}
The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich and Nir Sharon for helpful discussions, Fred Sigworth for supplying us with the dataset of the BPTI molecule,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
NB is partially supported by NSF award DMS-1719558.

>>>>

\section*{Acknowledgment}
The authors  thank Ayelet Heimowitz, Joe Kileel,  Roy Lederman, Amit Moscovich, Nir Sharon and  Fred Sigworth for helpful discussions,  and Boris Landa and Yoel Shkolnisky for providing the code for the 2-D PSWFs expansion.
The research was partially supported by Award Number R01GM090200 from the NIGMS, FA9550-17-1-0291 from AFOSR, Simons Foundation Math+X Investigator Award, and the Moore Foundation Data-Driven Discovery Investigator Award.
NB is partially supported by NSF award DMS-1719558.
